### 2023-02-24 appendices/appendix.tex
Sync-up

%!TEX root = ../thesis.tex
\chapter{An Appendix}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

%!TEX root = ../thesis.tex
\chapter[an appendix]{An Appendix}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

### 2023-02-24 frontmatter/notation.tex
Sync-up

\makenomenclature
%\markboth{\MakeUppercase\nomname}{\MakeUppercase\nomname}
% Correct header on multiple page nomenclature
\patchcmd{\thenomenclature}
  {\chapter*{\nomname}}% usually only \chapter*{\nomname} is issued
  {\chapter*{\nomname}\markboth{\MakeUppercase\nomname}{\MakeUppercase\nomname}}
  {}{}
% Rename Nomenclature to Notation
\renewcommand{\nomname}{Notation}
% Increase width of box for mathematical symbol on left
\setlength{\nomlabelwidth}{2.5cm}
% \setlength{\nomitemsep}{-\parsep}

% Command for the group subtitles
\newcommand{\nommenclaturesubtitle}[1]{%
    \bigskip
    \item[\bfseries \hspace{2.5cm}\: #1
        % \vspace{1cm}\\
        % \hspace{2.4cm} #1 \hfill\\
        % \par\noindent\rule{\widthof{#1}}{1pt}
    ]
    %\par\noindent\rule{\widthof{#1}}{1pt}%
    %   \hspace*{-\leftmargin}%
    %   \rule[2pt]{0.45\linewidth}{1pt}%
    %   \hfill #1\hfill
    %   \rule[2pt]{0.45\linewidth}{1pt}%
}

@@

\nomenclature[E, 01]{$\frac{\text{d}y}{\text{d}x}$}{Derivative of $y$ with respect to $x$}
\nomenclature[E, 02]{$\pderiv{y}{x}$}{Partial derivative of $y$ with respect to $x$}
\nomenclature[E, 03]{$\nabla_\x$}{Del, nabla or Laplacian operator, $\nabla_\x = \bmat{\pderiv{}{x_1} & \cdots & \pderiv{}{x_n}}^\text{T}, \; \x\in\mathbb{R}^{n}$}
\nomenclature[E, 04]{$\nabla_\x y$}{Gradient of $y$ with respect to $\x$, $\nabla_\x y = \bmat{\pderiv{y}{x_1} & \cdots & \pderiv{y}{x_n}}^\text{T}, \; \x\in\mathbb{R}^{n}$}
\nomenclature[E, 05]{$\H_\x$}{Hessian operator, $\H_\x = \nabla_\x\nabla_\x\transpose = \bmat{
	    \pderiv[2]{}{x_1} & \pderiv[1,1]{}{x_1,x_2} & \cdots & \pderiv[1,1]{}{x_1,x_n}\\
	    \pderiv[1,1]{}{x_2,x_1} & \pderiv[2]{}{x_2} & \cdots & \pderiv[1,1]{}{x_2,x_n}\\
	    \vdots & \vdots & \ddots & \vdots\\
	    \pderiv[1,1]{}{x_n,x_1} & \pderiv[1,1]{}{x_d,x_2} & \cdots & \pderiv[2]{}{x_n}
	    }$}
\nomenclature[E, 06]{$\H_\x y$}{Hessian matrix of $y$ with respect to $\x$; matrix of all second order partial derivatives}
\nomenclature[E, 07]{$\nabla^2_\x$}{Laplacian operator, $\nabla^2_\x=\nabla_\x\transpose\nabla_\x = \nabla_\x\cdot\nabla_\x=\sum_i \pderiv[2]{}{x_i}=\Tr{\H_\x}$}
\nomenclature[E, 08]{$\nabla^2_\x y$}{Laplacian of $y$ with respect to $\x$; sum of the unmixed second order partial derivatives}
\nomenclature[E, 09]{$\pderiv{\y}{\x}$}{Jacobian matrix of $\y$ w.r.t. $\x$, $\pderiv{\y}{\x} = \bmat{
	    \nabla_\x^\text{T} y_1\\
	    \vdots \\
	    \nabla_\x^\text{T} y_n}, \; \y\in\mathbb{R}^{n}$; matrix of all possible first order partial derivatives}
\nomenclature[E, 10]{$\int f(\x)\,\text{d}\x$}{Definite integral over the domain of $\x$}
\nomenclature[E, 11]{$\int_\mathcal{D} f(\x)\,\text{d}\x$}{Definite integral over the domain $\mathcal{D}$}

>>>>

\makenomenclature
%\markboth{\MakeUppercase\nomname}{\MakeUppercase\nomname}

% Correct header on multiple page nomenclature
\patchcmd{\thenomenclature}
  {\chapter*{\nomname}}% usually only \chapter*{\nomname} is issued
  {\chapter*{\nomname}\markboth{\MakeUppercase\nomname}{\MakeUppercase\nomname}}
  {}{}

\renewcommand{\nomname}{Notation}  % Rename Nomenclature to Notation

\setlength{\nomlabelwidth}{3cm}  % Increase width of box for mathematical symbol on left
% \setlength{\nomitemsep}{-\parsep}

% Command for the group subtitles
\newcommand{\nommenclaturesubtitle}[1]{%
    \bigskip
    \item[\bfseries \hspace{3cm}\: #1
        % \vspace{1cm}\\
        % \hspace{2.4cm} #1 \hfill\\
        % \par\noindent\rule{\widthof{#1}}{1pt}
    ]
    %\par\noindent\rule{\widthof{#1}}{1pt}%
    %   \hspace*{-\leftmargin}%
    %   \rule[2pt]{0.45\linewidth}{1pt}%
    %   \hfill #1\hfill
    %   \rule[2pt]{0.45\linewidth}{1pt}%
}

@@

\nomenclature[E, 01]{$\frac{\text{d}y}{\text{d}x}$}{Derivative of $y$ with respect to $x$}
\nomenclature[E, 02]{$\pd{y}{x}$}{Partial derivative of $y$ with respect to $x$}
\nomenclature[E, 03]{$\nabla_\x$}{Del, nabla or Laplacian operator, $\nabla_\x = \bmat{\pd{}{x_1} & \cdots & \pd{}{x_n}}^\text{T}, \; \x\in\mathbb{R}^{n}$}
\nomenclature[E, 04]{$\nabla_\x y$}{Gradient of $y$ with respect to $\x$, $\nabla_\x y = \bmat{\pd{y}{x_1} & \cdots & \pd{y}{x_n}}^\text{T}, \; \x\in\mathbb{R}^{n}$}
\nomenclature[E, 05]{$\H_\x$}{Hessian operator, $\H_\x = \nabla_\x\nabla_\x\transpose = \bmat{
	    \pd[2]{}{x_1} & \frac{\partial^2}{\partial x_1 \partial x_2} & \cdots & \frac{\partial^2}{\partial x_1 \partial x_n}\\
	    \frac{\partial^2}{\partial x_2 \partial x_1} & \pd[2]{}{x_2} & \cdots & \frac{\partial^2}{\partial x_2 \partial x_n}\\
	    \vdots & \vdots & \ddots & \vdots\\
	    \frac{\partial^2}{\partial x_n \partial x_1} & \frac{\partial^2}{\partial x_n \partial x_2} & \cdots & \pd[2]{}{x_n}
	    }$}
\nomenclature[E, 06]{$\H_\x y$}{Hessian matrix of $y$ with respect to $\x$; matrix of all second order partial derivatives}
\nomenclature[E, 07]{$\nabla^2_\x$}{Laplacian operator, $\nabla^2_\x=\nabla_\x\transpose\nabla_\x = \nabla_\x\cdot\nabla_\x=\sum_i \pd[2]{}{x_i}=\Tr{\H_\x}$}
\nomenclature[E, 08]{$\nabla^2_\x y$}{Laplacian of $y$ with respect to $\x$; sum of the unmixed second order partial derivatives}
\nomenclature[E, 09]{$\pd{\y}{\x}$}{Jacobian matrix of $\y$ w.r.t. $\x$, $\pd{\y}{\x} = \bmat{
	    \nabla_\x y_1 &
	    \cdots &
	    \nabla_x y_n}^\text{T}, \; \y\in\mathbb{R}^{n}$; matrix of all possible first order partial derivatives}
\nomenclature[E, 10]{$\int f(\x)\,\text{d}\x$}{Definite integral over the domain of $\x$}
\nomenclature[E, 11]{$\int_\mathcal{D} f(\x)\,\text{d}\x$}{Definite integral over the domain $\mathcal{D}$}
